On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/experiments.tex
Table fixes - put the values of acc in the right place
Modified table with finetuning on CoGenT-B

\begin{table}[]
	\caption{CLEVR \& CoGenT accuracies for the MAC \& simplified MAC models}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		\multirow{3}{*}{MAC}  & CLEVR                       & 31.86         &  --   & --                     & 96.7                  & CLEVR    & 96.2          \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31.86}     &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{97.0} & CoGenT-A & 96.9         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B & 79.5          \\
		\midrule
		\multirow{3}{*}{SMAC} & CLEVR                       & 28.51      &   --   &   --                 & 95.8               & CLEVR    & 95.3          \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28.55}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{96.1} & CoGenT-A & 95.9          \\
		\cmidrule{7-8} 
		&                             &                                         &     &          &                & CogenT-B & 78.7          \\
		\bottomrule
	\end{tabular}
	\label{results}
\end{table}

>>>>

\begin{table}[]
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		\multirow{10}{*}{MAC} & \multirow{4}{*}{CLEVR}  & \multirow{4}{*}{30:52}  & \multirow{4}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
		\cmidrule{7-8} 
		 &                        &  &               &     &                                & CoGenT-A    &  96.22   \\
		\cmidrule{7-8} 
		  &                        &   &              &     &                               & CoGenT-B   & 96.27  \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
		\midrule
		\multirow{10}{*}{S-MAC} & \multirow{3}{*}{CLEVR}  & \multirow{3}{*}{28:30}  & \multirow{3}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\		
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
		\cmidrule{7-8} 
		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  x         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    x       \\
		\bottomrule
	\end{tabular}
	\label{results}
\end{table}
